Abstract Binding Trees

### 2015-11-01 paper.tex
update pdf
fix typo

% fonts
\usepackage[
  activate={true,nocompatibility},
  draft,
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

@@

%%TODO
We also have an induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma_{\Upsilon\parallel\Gamma}}{A^{\Yoneda{\Upsilon\parallel\Gamma}} \times
Y^{\{\Upsilon\}}\times A^{[\Gamma]}}$.

>>>>

% fonts
\usepackage[
  activate={true,nocompatibility},
  final,
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

@@

%%TODO
We also have an induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma_{\Upsilon\parallel\Gamma}}{P_s^{\Yoneda{\Upsilon\parallel\Gamma}} \times
Y^{\{\Upsilon\}}\times P^{[\Gamma]}\to P_s}$.
